\section{Results}
\label{sec:results}

In this section, we discuss results of our experiments. We specifically
discuss our
results from a sample size of 500 out of the many sample sizes. 
Table \ref{tab:auto2}-\ref{tab:coc10000} shows some of our results. For
more results, please refer to the GitHub repository.

\subsection{Sway1 vs. Sway2}
  We
  observe that adding randomness in our model achieved mixed results. In
  most cases, sway2 performs slightly worse or similarly to sway1.
  However, there are certain cases where sway2 performs better. For
  example, sway2 performs better when we try to maximize \textit{Kloc} for
  the \textit{nasa93dem} dataset. We indicate objectives where sway2
  performs better than as red in our tables. As sway2 introduces
  randomness, we can infer that 
  for these objectives, closely clustered data points based on the x
  columns do not necessarily relate to similar values for the objectives.
  For example, in table \ref{tab:coc1000}, closely clustered x columns
  for coc1000 may not
  have similar values for the \textit{Effort} objective. 
  The same can be seen in table \ref{tab:nasa93dem} and
  \ref{tab:coc10000}.
  Results labeled top are results yielded from comparing all data.
  Logically, this returned the best results, however it is also the most
  time-consuming method. Comparing sway to top, we observe that there is
  a noticeable decrease in performance, this is often referred to as the
  \textit{sampling tax}. This shows we sacrifice the optimal values for
  in exchange for time when implementing sway. 
  
\subsection{Xpln}
  We applied sway1 and sway2 to xpln, which we labeled as xpln1 and
  xpln2 in our tables. As shown from the tables, for most cases, xpln
  performs slightly worse than sway along. This loss in performance is
  the \textit{explanation tax}. This is due to the fact that xpln uses
  simpler rules to distinguish the data points. However, there are cases
  in which xpln performs better than sway, we infer that this shows that
  data for certain features can be clustered using simpler rules. We
  highlighted cases where xpln performs better than sway in blue in
  tables \ref{tab:auto2}, \ref{tab:coc1000}, \ref{tab:coc10000}.
  Understanding phenomenon like this could be useful where we would
  conduct future studies, as we discuss in section \ref{sec:bonus_february}.

\subsection{Sample size}
\label{ssec:sample_size}
  We also conducted experiments with different sample sizes in an attempt
  to achieve better results with more samples. However, we did not observe
  a clear correlation between sample sizes and the objectives. Table
  \ref{tab:sample_nasa93dem} shows varying sample sizes for the
  \textit{nasa93dem} dataset. Upon receiving these results, we went back
  to check how sample size was implemented in the code. Sample size has an
  effect when selecting the two points when splitting data into two
  halves. The first point is selected at random, and the second point is
  selected from a group of data that is of sample size. However, that is
  the extent of which sample size has an effect. Thus, we infer that
  sample size does not have enough effect in our code to influence the
  results. 

\subsection{Effect size and Significance tests}
  With results from different models, we conducted the effect size test
  using cliff's delta and the significance test using bootstrap. The
  effect size test tests for relationship between two sets of data. We set
  the threshold to 0.4 for medium effects. The confidence for the
  significance test is set to 0.05. The conjunction of the two test
  between different results is shown in table \ref{tab:tests}. For those
  where the conjunction is =, this means both tests return true,
  which we can infer to meaning the two results are similar. We observe
  that results from sway1 are similar to results from sway2. However, both
  results from sway are not similar to results from top, due to sampling
  tax. It can also be
  seen from the table that xpln returns slightly different results from
  sway. 

\begin{table}[]
  \begin{center}
  \begin{tabular}{lllll}
          & CityMPG+      & Class-     & HighwayMPG+ & Weight-   \\
    \hline
    sway1 & 26.02         & 13.75      & 32.38       & 2661.03 \\
    xpln1 & \myblue{27.07}   & 16.17      & 33.14       & 2632.12   \\
    sway2 & 24.363        & 16.86      & 31.25       & 2845.97   \\
    xpln2 & \myblue{25.26}  & 16.72      & 25          & 2781.65   \\
    top   & 37.16         & 9.26       & 41.75       & 2040.98    
  \end{tabular}
  \end{center}
  \caption{Results for auto2.csv}
  \label{tab:auto2}
\end{table}


\begin{table}[]
  \begin{center}
  \begin{tabular}{llll}
        & Lbs-    & Acc+  & Mpg+  \\
  \hline
  sway1 & 2240.94 & 16.80 & 29.51 \\
  xpln1 & 2416.26 & 15.44 & 26.40 \\
  sway2 & 2319.56 & 16.62 & 29.72 \\
  xpln2 & 2456.19 & 14.49 & 23.57 \\
  top   & 1998.07 & 19.77 & 40.76
  \end{tabular}
\end{center}
  \caption{Results for auto93.csv}
  \label{tab:auto93}
\end{table}


% \begin{table}[]
%   \begin{center}
%   \begin{tabular}{ll}
%         & N\_effort- \\
%   \hline
%   sway1 & 1800.38    \\
%   xpln1 & 2619.90    \\
%   sway2 & 1965.81    \\
%   xpln2 & 2431.86    \\
%   top   & 145.94    
%   \end{tabular}
%   \end{center}
%   \caption{Results for china.csv}
%   \label{tab:china}
% \end{table}


\begin{table}[]
  \begin{center}
  \begin{tabular}{llllll}
        & LOC+    & AEXP- & PLEX- & RISK- & Effort-  \\
  \hline
  sway1 & 1027.74 & 3.05  & 2.88  & 5.08  & 29321.05 \\
  xpln1 & 913.11  & \myblue{2.67}  & \myblue{2.73}  & 5.7 & 27416.45 \\
  sway2 & 999.59  & \myred{2.92}  & 3.02  & 6.12  & \myred{28323.93} \\
  xpln2 & 918.43  & \myred{2.66}  & \myblue{2.73}  & 6.0   & \myred{26910.59} \\
  top   & 1571.43 & 1.62  & 1.39  & 4.7   & 35116.16
  \end{tabular}
\end{center}
\caption{Results for coc1000.csv}
\label{tab:coc1000}
  \end{table}

\begin{table}[]
  \begin{center}
    \begin{tabular}{lllll}
          & Kloc+ & Effort- & Defects- & Months-   \\
    \hline
    sway1 & 70.52 & 428.92  & 2811.09  & 20.86 \\
    xpln1 & 72.85 & 450.05  & 2894.04  & 21.40     \\
    sway2 & \myred{85.92} & 524.90  & 3289.46  & 22.04     \\
    xpln2 & \myred{84.24} & 542.82  & 3374.83  & 22.59     \\
    top   & 4.59  & 18.29   & 143.51   & 8.24     
    \end{tabular}
  \end{center}
  \caption{Results for nasa93dem.csv}
  \label{tab:nasa93dem}
\end{table}

\begin{table}[]
  \begin{center}
    \begin{tabular}{lllll}
          & MRE- & ACC+ & PRED40+   \\
    \hline
    sway1 & 74.71 & 7.40 & 19.215  \\
    xpln1 & 75.03 & 7.28 & 19.18     \\
    sway2 & 75.37 & 7.32 & 18.23     \\
    xpln2 & 75.03 & 7.27 & 19.24         
    \end{tabular}
  \end{center}
  \caption{Results for healthCloseIsses12mths0001-hard.csv}
  \label{tab:health-hard}
\end{table}

\begin{table}[]
  \begin{center}
    \begin{tabular}{lllll}
          & MRE- & ACC+ & PRED40+   \\
    \hline
    sway1 & 31.37 & -0.39 & 57.53   \\
    xpln1 & 35.96 & -0.46 & 53.85     \\
    sway2 & 26.03 & -0.46 & 62.11      \\
    xpln2 & 35.96 & -0.46 & 53.85          
    \end{tabular}
  \end{center}
  \caption{Results for healthCloseIsses12mths0011-easy.csv}
  \label{tab:health-easy}
\end{table}

% \begin{table}[]
%   \begin{center}
%     \begin{tabular}{lllll}
%           & PSNR-  &   Energy-    \\
%     \hline
%     sway1 & 44.48  &   1126.28   \\
%     xpln1 & 44.29  &   1621.32     \\
%     sway2 & 44.21  &   1612.90      \\
%     xpln2 & 44.46  &   1640.16          
%     \end{tabular}
%   \end{center}
%   \caption{Results for SSN.csv}
%   \label{tab:ssn}
% \end{table}


% \begin{table}[]
%   \begin{center}
%     \begin{tabular}{lllll}
%           & NUMBERITERATIONS-    \\
%     \hline
%     sway1 & 5.37   \\
%     xpln1 & 10.20     \\
%     sway2 & 6.27      \\
%     xpln2 & 9.37         
%     \end{tabular}
%   \end{center}
%   \caption{Results for SSM.csv}
%   \label{tab:ssm}
% \end{table}

\begin{table}[]
  \begin{center}
    \begin{tabular}{lllll}
          & LOC+   &    RISK- &   EFFORT-     \\
    \hline
    sway1 & 1004.94&    5.22   &  26372.00  \\
    xpln1 & 604.81  &   \myblue{4.02}  &  \myblue{17308.46}   \\
    sway2 & 1006.16  &  \myred{4.57}   &  \myred{24570.96}      \\
    xpln2 & 454.17   &  \myred{2.71}   &  \myred{13859.63}        
    \end{tabular}
  \end{center}
  \caption{Results for coc10000.csv}
  \label{tab:coc10000}
\end{table}


\begin{table}[]
  \begin{center}
  \begin{tabular}{lllll}
       & Kloc+  & Effort- & Defects- & Months- \\
  \hline
  10   & 70.52  & 329.06  & 2038.96  & 19.09   \\
  25   & 47.925 & 250.97  & 1743.88  & 17.87   \\
  50   & 64.64  & 311.22  & 2427     & 20.08   \\
  100  & 62.24  & 314.84  & 2325.34  & 19.14   \\
  200  & 94.33  & 602.88  & 3629.39  & 24.35   \\
  500  & 86.29  & 489.42  & 3323.69  & 22.12   \\
  1000 & 106.19 & 635.1   & 4117.55  & 25.47  
  \end{tabular}
\end{center}
\caption{Results for different sample size for nasa93dem.csv}
\label{tab:sample_nasa93dem}
\end{table}


\begin{table*}[h]
  \begin{center}
    \input{figures/test_subset.tex}
  \end{center}
  \caption{Results for effect size test and significance test}
\label{tab:tests}
\end{table*}
